Meta-analytic approaches and effect sizes to account for 'nuisance heterogeneity' in comparative physiology

### 2021-09-17 MS/ms.Rmd
Fixed figure so that weighted models are now coloured

    # If you have issues with flextable and equatags, make sure you have node.js and use mathjax_install(). See here:https://github.com/ardata-fr/equatags
  pacman::p_load(flextable, tidyverse, equatags, png, magick)  
```

@@

```{r, figsurv, fig.wid = 16.833333, fig.height=5,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use. (B) Frequency of studies where ‘nuisance heterogenity’ had the potential to impact effect sizes (x-axis), and the frequencies of studies explicitly dealing with nuisance heterogeneity (bar colour). (C) Frequencies of analytical approaches used to analyse effect measures. Note that only ‘Weighted Regression’, ‘Random Effects Models’, ‘Multilevel Metaregression Models’ and ‘Multilevel Meta-analysis Models’ are weighted models. The results of this survey were drawn from 62 studies in comparative physiology."}
p1 = dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type)  %>% 
  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
                 Mean = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
  mutate(effect = fct_relevel(effect, c("Other", "Zr", "lnRR", "SMD", "lnCVR", "Slope", "Mean"))) %>% 
  ggplot() + tm + 
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,0.35)) +
  labs(x = "Effect Size",
       y = "Frequency") +
  coord_flip()

@@

p3 <- summary %>% 
  mutate(effect = fct_relevel(effect, c("Other","Vote Counting", "Linear Regression", "Weighted Regression", "Random Effects Model", "Multilevel Meta-analysis Model", "Multilevel Metaregression Model"))) %>% 
  ggplot() + tm +
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
  labs(x = "Analytical Approach",
       y = "Frequency") +
  coord_flip()

>>>>

    # If you have issues with flextable and equatags, make sure you have node.js and use mathjax_install(). See here:https://github.com/ardata-fr/equatags
  pacman::p_load(flextable, tidyverse, equatags, png, magick, RColorBrewer)  
```

@@

```{r, figsurv, fig.wid = 16.833333, fig.height=5,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use. (B) Frequency of studies where ‘nuisance heterogenity’ had the potential to impact effect sizes (x-axis), and the frequencies of studies explicitly dealing with nuisance heterogeneity (bar colour). (C) Frequencies of analytical approaches used to analyse effect measures. 'Orange' bars indicate weighted models. The results of this survey were drawn from 62 studies in comparative physiology."}
p1 = dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type)  %>% 
  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
                 Mean = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
  mutate(effect = fct_relevel(effect, c("Other", "Zr", "lnRR", "SMD", "lnCVR", "Slope", "Mean"))) %>% 
  ggplot() + tm + 
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,0.35)) +
  labs(x = "Effect Size",
       y = "Frequency") +
  coord_flip()

@@

p3 <- summary %>% 
  mutate(effect = fct_relevel(effect, c("Other","Vote Counting", "Linear Regression", "Weighted Regression", "Random Effects Model", "Multilevel Meta-analysis Model", "Multilevel Metaregression Model")),
              col = c("#66C2A5", "#8DA0CB", "#8DA0CB", "#66C2A5", "#8DA0CB", "#66C2A5", "#8DA0CB")) %>% 
  ggplot() + tm +
  geom_col(aes(x = effect, y = prop, fill = col), width = 0.5,colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
  scale_fill_brewer(palette = "Set2") + 
  labs(x = "Analytical Approach",
       y = "Frequency") +
  theme(legend.position = "none") +
  coord_flip()
